Microlensing as a possible probe of the internal structure of quasars

### 2015-07-18 paper1/fitting.tex
small edits

The crescent source had parameters (as explained in
\S\ref{subsec:crescent}) $R_p$ and $R_n$ being the radii of the outer
and inner circles and $(\alpha,\beta)$ being the coordinates of the inner
circle with respect to the centre of the outer circle in the coordinate system associated with the image in Figure 1 and not associated 
with the caustic surface as defined in the previous sections.  The parameter values were
\begin{equation}
   (R_p, R_n, $\alpha$, $\beta$) = (50.0, 30.0, 15.0, 10.0).
\label{eqn:cp}
\end{equation}
The uniform disc had the same (outer) radius as the crescent.  In the
Gaussian source, we set $3\sigma=50$.  For convenience, below we will
refer to $R_p$ of the Gaussian source, by which we actually mean
$3\sigma$.

@@

Figure~\ref{fig:mockdata} shows the three light curves.  Each has
250 points regularly spaced in time, with Gaussian noise at the level
of 10\% of the current brightness.  The effective signal to noise can
be considered to be \textbf{ bad math here -- $0.1\times\sqrt{250}\simeq150$}.

@@

Let us first consider the three cases where a crescent model was
fitted.  These are the solid curves in Figure~\ref{fig:mcmc}, with the
colours of the curves indicating the source.  Meanwhile,
Figure~\ref{fig:crescentfit} shows $2\sigma$ of the inferred parameter
values. \textbf{In the following enumerated conclusions we associate the word "wrong"
with parameters for which the real value corresponds to a PDF of the fitted model smaller than 
0.01. }

@@

\item[3) {\bf CG}:] Solid green curve and green ellipses.
  Additionally, Figure~\ref{fig:burnin} shows the progress of
  reduction of $\chi^2$ in this case, where a crescent-source model is
  used to fit data from a Gaussian source.  The parameter values are
  seemingly tightly constrained, but the recovered $R_p$ is completely
  wrong.  The reduced $\chi^2$ is only 0.85, indicative of
  over-fitting.  We can see what has happened from the red curve in
  the bottom panel of Figure~\ref{fig:mockdata}.  The best-fit model
  covers only a small part of the light curve.  That is, the fitting
  procedure has exploited the nuisance parameters to find a good fit
  to mainly noise.

>>>>

The crescent source had parameters (as explained in
\S\ref{subsec:crescent}) $R_p$ and $R_n$ being the radii of the outer
and inner circles and $(\alpha,\beta)$ being the coordinates of the inner
circle with respect to the centre of the outer circle in the coordinate system associated with the image in Figure 1 and not associated 
with the caustic surface as defined in the previous sections.  The parameter values were
\begin{equation}
   (R_p, R_n, \alpha, \beta) = (50.0, 30.0, 15.0, 10.0).
\label{eqn:cp}
\end{equation}
The uniform disc had the same (outer) radius as the crescent.  In the
Gaussian source, we set $3\sigma=50$.  For convenience, below we will
refer to $R_p$ of the Gaussian source, by which we actually mean
$3\sigma$.

@@

Figure~\ref{fig:mockdata} shows the three light curves.  Each has 250
points regularly spaced in time, with Gaussian noise at the level of
10\% of the current brightness.  The effective signal to noise can be
considered to be $0.1\times\sqrt{250}\simeq15$.

@@

Let us first consider the three cases where a crescent model was
fitted.  These are the solid curves in Figure~\ref{fig:mcmc}, with the
colours of the curves indicating the source.  Meanwhile,
Figure~\ref{fig:crescentfit} shows $2\sigma$ of the inferred parameter
values.

@@

\item[3) {\bf CG}:] Solid green curve and green ellipses.
  Additionally, Figure~\ref{fig:burnin} shows the progress of
  reduction of $\chi^2$ in this case, where a crescent-source model is
  used to fit data from a Gaussian source.  The parameter values are
  seemingly tightly constrained, but the recovered $R_p$ is completely
  wrong, since the correct value is far from the green curve and green
  ellipses.  The reduced $\chi^2$ is only 0.85, indicative of
  over-fitting.  We can see what has happened from the red curve in
  the bottom panel of Figure~\ref{fig:mockdata}.  The best-fit model
  covers only a small part of the light curve.  That is, the fitting
  procedure has exploited the nuisance parameters to find a good fit
  to mainly noise.
